% =====================================================================
%  CV — Ana Sofia Arango Yanza  (English version)
%  Recommended compiler: XeLaTeX
%  Style: modern minimalist — single column, ATS-friendly
% =====================================================================

\documentclass[11pt,a4paper]{article}

% ----- Page geometry -----
\usepackage[
  a4paper,
  top=1.4cm,
  bottom=1.4cm,
  left=1.6cm,
  right=1.6cm
]{geometry}

% ----- Encoding -----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

% ----- Typography -----
\usepackage[default,scale=0.95]{sourcesanspro}

% ----- Colors -----
\usepackage{xcolor}
\definecolor{accent}{HTML}{C7385A}
\definecolor{ink}{HTML}{1a1a1a}
\definecolor{muted}{HTML}{6b6b6b}
\definecolor{rule}{HTML}{d4d4d4}

% ----- Headings and rules -----
\usepackage{titlesec}
\titleformat{\section}
  {\color{ink}\large\bfseries\MakeUppercase}
  {}{0pt}{}
  [\vspace{2pt}\color{rule}\titlerule\vspace{4pt}]
\titlespacing*{\section}{0pt}{12pt}{4pt}

% ----- Links -----
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=ink,
}

% ----- Compact lists -----
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt, label={\color{accent}$\bullet$}}

% ----- No page numbers -----
\pagestyle{empty}

% ----- CV helpers -----
\newcommand{\cventry}[4]{%
  \noindent\textbf{\color{ink}#1}\hfill{\color{muted}\small#2}\\
  {\color{ink}\itshape#3}\hfill{\color{muted}\small#4}\par
  \vspace{2pt}
}

\newcommand{\cvaward}[3]{%
  \noindent{\color{ink}#1}\hfill{\color{muted}\small#3}\\
  {\color{muted}\small#2}\par\vspace{4pt}
}

% Project: #1 title+role, #2 date/link, #3 subtitle/client, #4 bullets, #5 stack
\newcommand{\cvproject}[5]{%
  \noindent\textbf{\color{ink}#1}\hfill{\color{muted}\small#2}\\
  {\color{accent}\small\itshape#3}\par
  \vspace{1pt}
  {\color{ink}#4}
  \vspace{1pt}\par
  {\color{muted}\small\textbf{Tech:} #5}\par\vspace{6pt}
}

% Skill row: #1 category, #2 list
\newcommand{\cvskill}[2]{%
  \noindent{\color{ink}\small\textbf{#1}}\hspace{0.4em}{\color{muted}\small#2}\par\vspace{2pt}
}

\setlength{\parindent}{0pt}

% =====================================================================
\begin{document}

% =====================================================================
%  HEADER
% =====================================================================
\begin{center}
  {\huge\bfseries\color{ink} Ana Sofia Arango Yanza}\\[4pt]
  {\color{muted}\small
    Popayán, Colombia\ \textbullet\
    \href{mailto:sofiaarango141@gmail.com}{sofiaarango141@gmail.com}\
    \textbullet\ +57 310 668 3378
  }\\[2pt]
  {\color{muted}\small
    \href{https://ana-sofia-arango.vercel.app}{ana-sofia-arango.vercel.app}\
    \textbullet\
    \href{https://linkedin.com/in/ana-sofia-arango}{linkedin.com/in/ana-sofia-arango}\
    \textbullet\
    \href{https://github.com/Sofii141}{github.com/Sofii141}
  }
\end{center}

\vspace{4pt}

% =====================================================================
%  SUMMARY
% =====================================================================
\section*{Summary}
{\color{ink}
Systems Engineering student (9th semester, GPA 4.5/5.0) and full-stack developer
with experience leading software projects for public-sector clients and building
generative-AI solutions with LLMs and multi-agent systems. Passionate about
detail, product design, and the intersection of software engineering and
artificial intelligence. Bilingual (Spanish / English).
}

% =====================================================================
%  EDUCATION
% =====================================================================
\section*{Education}

\cventry
  {Universidad del Cauca}{Aug. 2022 -- Jun. 2027 (expected)}
  {B.Sc. in Systems Engineering}{Popayán, Colombia}

\vspace{-2pt}
{\color{ink}\small GPA: \textbf{4.5 / 5.0} \textbullet\ Currently in 9th semester}

% =====================================================================
%  HONORS & AFFILIATIONS
% =====================================================================
\section*{Honors \& Affiliations}

\cvaward
  {Dean's List Scholarship (Matrícula de Honor) — Universidad del Cauca}
  {Awarded three times for outstanding academic performance.}
  {2023 -- 2026}

\cvaward
  {\textbf{First Place} — ``Innovation in Action'' category}
  {First Academic Projects Fair \& 4th Alumni Meeting, Systems Engineering Program — Universidad del Cauca.}
  {Apr. 2026}

\cvaward
  {Speaker — ``Dementia-Level Classification on MRI Images with Deep Learning''}
  {Poster and paper presented at the First Academic Projects Fair, Universidad del Cauca.}
  {Apr. 2026}

\cvaward
  {Speaker — ``Bayesian Optimization of a Convolutional Neural Network for P-Wave Detection''}
  {Poster presented at the 5th \emph{Ciencia al Parque} Meeting, Cauca Research Board.}
  {Dec. 2025}

\cvaward
  {Active Member — Data Science Research Group}
  {Universidad del Cauca. Participation in research projects and academic events.}
  {2025 -- Present}

\cvaward
  {Active Member — IEEE Student Branch, Universidad del Cauca}
  {Support in organizing academic and technical events.}
  {2025 -- Present}

% =====================================================================
%  FEATURED PROJECTS
% =====================================================================
\section*{Featured Projects}

\cvproject
  {Vigía Cauca — Team Lead \& Full-Stack Developer}
  {2026}
  {Web platform for the Cauca Government Secretariat (regional government)}
  {\begin{itemize}
    \item Led the development team across every stage of the project, from requirements gathering to formal client handover.
    \item Built the frontend (React + Leaflet) and backend (Spring Boot + PostgreSQL) of a geo-referenced security-incident management system under a hexagonal, microservices architecture.
    \item Implemented role-based authentication, interactive dashboards with heat maps, and exportable reports (PDF / Excel), with CI/CD on GitHub Actions.
  \end{itemize}}
  {React, Leaflet, Spring Boot, Java, PostgreSQL, Docker, GitHub Actions}

\cvproject
  {AIMO — Full-Stack \& AI Developer}
  {2026 \textbullet\ \href{https://aimo-amber.vercel.app}{aimo-amber.vercel.app}}
  {Conversational emotional-support assistant for university students}
  {\begin{itemize}
    \item Built a cascading multi-agent system with LLMs (LLaMA 3.3-70B, GPT-4, Claude Sonnet 4.5) using the \emph{LLM-as-a-Judge} methodology to assess empathy in real time.
    \item Developed the backend (Python + Flask) integrating multiple AI providers (Groq, OpenAI, AWS Bedrock) and the frontend (React + Vite).
    \item Deployed the full-stack application to production (Vercel + Railway).
  \end{itemize}}
  {Python, Flask, React, LLMs, Groq, OpenAI, AWS Bedrock}

\cvproject
  {Personal Portfolio}
  {2026 \textbullet\ \href{https://ana-sofia-arango.vercel.app}{ana-sofia-arango.vercel.app}}
  {Editorial personal site with full-page navigation and animations}
  {\begin{itemize}
    \item Designed and built a portfolio with a full-page navigation system, slideshow-style transitions, bilingual support (ES / EN), and multiple color themes.
  \end{itemize}}
  {Next.js 15, React 19, TypeScript, Tailwind CSS, Framer Motion}

% =====================================================================
%  TECHNICAL SKILLS
% =====================================================================
\section*{Technical Skills}

\cvskill{Languages}{Java, Python, TypeScript, JavaScript, C\#, SQL, HTML5, CSS3}
\cvskill{Frontend}{React, Next.js, Angular, React Native, Tailwind CSS, Leaflet}
\cvskill{Backend}{Spring Boot, Flask, Node.js, ASP.NET Core, REST APIs}
\cvskill{AI / Data}{LLMs, multi-agent systems, prompt engineering, TensorFlow, Scikit-learn, OpenAI, AWS Bedrock, Groq}
\cvskill{Databases}{PostgreSQL, MySQL, MongoDB, Oracle, Entity Framework}
\cvskill{Cloud \& DevOps}{AWS, Vercel, Railway, Docker, Git, GitHub Actions}
\cvskill{Architecture}{Microservices, hexagonal, onion, atomic design}
\cvskill{Tools}{Git, GitHub, Figma}

% =====================================================================
%  CERTIFICATIONS
% =====================================================================
\section*{Certifications}

\cvskill{NVIDIA Deep Learning Institute}{Rapid Application Development with LLMs \textbullet\ Building LLM Applications with Prompt Engineering \textbullet\ Generative AI Explained \textbullet\ Transformer-Based NLP \textbullet\ Getting Started with Deep Learning \textbullet\ Accelerating End-to-End Data Science Workflows}
\vspace{2pt}
\cvskill{Cisco Networking Academy}{CCNA: Introduction to Networks \textbullet\ CCNA: Switching, Routing \& Wireless Essentials \textbullet\ Junior Cybersecurity Analyst Career Path \textbullet\ Introduction to Cybersecurity}

% =====================================================================
%  LANGUAGES
% =====================================================================
\section*{Languages}

\cvskill{Spanish}{Native}
\cvskill{English}{Intermediate (B1-B2) — fluent technical reading and writing}

\end{document}
